On the performance of the MAC model

### 2018-10-31 2018_nips_vigil/experiments.tex
Added MIP bib position, cleaned up the imported packages, refactored table so it is consistent with NIPS guidelines

We propose to further analyze MAC's generalization and transfer learning abilities by testing it on the CLEVR-CoGenT dataset. It is synthesized in the same way as CLEVR but contains two conditions: in Condition A, all cubes are gray, blue, brown, or yellow and all cylinders are red, green, purple, or cyan; in Condition B, cubes and cylinders swap color palettes. Both conditions contain spheres of all colors. We also evaluate the simplified model on this dataset for comparison.

@@

We implemented the models using PyTorch\footnote{\url{https://pytorch.org/}} (v0.4.0), and the code is available on GitHub\footnote{\url{https://github.com/IBM/mi-prometheus/}}. The system is based on Linux 16.04 and we used NVIDIA's GeForce GTX TITAN X. We followed the implementation details indicated in the original paper (Section A of the supplementary material), to ensure a faithful comparison.

\begin{table}[]
	\centering
	\begin{tabular}{|c|c|c|c|c|c|}
		\hline
		Model                 & Training set                & \multicolumn{1}{l|}{Training wall time} & Training statistics          & Test set & Test statistics \\ \hline
		\multirow{3}{*}{MAC}  & CLEVR                       & 31h                                     & acc: 96.7\%                  & CLEVR    & 96.2\%          \\ \cline{2-6} 
		& \multirow{2}{*}{CoGenT - A} & \multirow{2}{*}{31h}                    & \multirow{2}{*}{acc: 97.0\%} & CoGenT-A & 96.9\%          \\ \cline{5-6} 
		&                             &                                         &                              & CoGenT-B & 79.5\%          \\ \hline
		\multirow{3}{*}{SMAC} & CLEVR                       & 28h                                     & acc: 95.8.\%                 & CLEVR    & 95.3\%          \\ \cline{2-6} 
		& \multirow{2}{*}{CoGenT-A}   & \multirow{2}{*}{28h}                    & \multirow{2}{*}{acc: 96.1\%} & CoGenT-A & 95.9\%          \\ \cline{5-6} 
		&                             &                                         &                              & CogenT-B & 78.7\%          \\ \hline
	\end{tabular}
	\caption{CLEVR \& CLEVR-CoGenT accuracy for the MAC \& simplified MAC model.}
	\label{results}
\end{table}

>>>>

We analyze MAC's generalization and transfer learning abilities by testing it on the CLEVR-CoGenT dataset. It is synthesized in the same way as CLEVR, but contains two conditions: in Condition A, all cubes are gray, blue, brown, or yellow and all cylinders are red, green, purple, or cyan; in Condition B, cubes and cylinders swap color palettes. Both conditions contain spheres of all colors. We also evaluate the simplified model on this dataset for comparison.

@@

We implemented both versions of the MAC model using PyTorch v0.4.0~\cite{paszke2017automatic}. We relied on the MI-Prometheus~\cite{kornuta2018accelerating} framework for training and testing of both models\footnote{The code of models along with training settings are available on \url{https://github.com/IBM/mi-prometheus/}}. For training we have used NVIDIA's GeForce GTX TITAN X. We followed the implementation details indicated in the original paper~\cite{hudson2018compositional} (Section A of the supplementary material), to ensure a faithful comparison.

\begin{table}[]
	\caption{CLEVR \& CoGenT accuracies for the MAC \& simplified MAC models}
	\centering
	\begin{tabular}{cccccc}
		\toprule
		Model                 & Training set                & Training time [h] & Training acc [\%]          & Test set & Test acc [\%] \\
		\midrule
		\multirow{3}{*}{MAC}  & CLEVR                       & 31                                   & acc: 96.7                  & CLEVR    & 96.2          \\
		\cmidrule{2-6} 
		& \multirow{2}{*}{CoGenT-A} & \multirow{2}{*}{31}                    & \multirow{2}{*}{acc: 97.0} & CoGenT-A & 96.9         \\
		\cmidrule{5-6} 
		&                             &                                         &                              & CoGenT-B & 79.5          \\
		\midrule
		\multirow{3}{*}{SMAC} & CLEVR                       & 28                                     & acc: 95.8               & CLEVR    & 95.3          \\
		\cmidrule{2-6} 
		& \multirow{2}{*}{CoGenT-A}   & \multirow{2}{*}{28}                    & \multirow{2}{*}{acc: 96.1} & CoGenT-A & 95.9          \\
		\cmidrule{5-6} 
		&                             &                                         &                              & CogenT-B & 78.7          \\
		\bottomrule
	\end{tabular}
	\label{results}
\end{table}
